Working title: Ecological network control

### 2018-05-25 paper/manuscript.Rmd
Describe things to do in methods

We then examined whether any species-level structural properties could predict a species control capacity $\phi$ and the likelihood of being a superior node.
Still need to decide how to do this and how to compare traditional centrality metrics to the new control based ones.

>>>>

We then examined whether any species-level structural properties could predict a species control capacity $\phi$ and the likelihood of being a superior node.
*TODO: Still need to decide how to do this and how to compare traditional centrality metrics to the new control based ones. Will probably base the comparision on stability/feasibility metrics or/and on coextinction of species groups.*
